Optiplan proposal

### 2018-07-10 R/presentations/MOSIM_presentation/presentation.Rmd
adapted MOSIM html presentation.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
# exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
# gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

### 2018-07-10 R/presentations/OptiPlan_presentation/proposal_fr.Rmd
adapted MOSIM html presentation.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('functions/params.R')
source('functions/import_results.R')
source('diagrams/cases.R')
source("diagrams/architecture.R")
source("diagrams/functionalities.R")
source('functions/exampleDT.R')
source('functions/gantt_tasks.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
exp_directory2 = PATHS[['experiments']] %>% paste0('201802061201/')
gantt <- print_solution(exp_directory, max_resources = 10, width="100%", height="500px")
gantt_tasks <- print_tasks(exp_directory2, width="100%", height="200px", max_tasks = 5)
graphs_rem <- graph_remaining(exp_directory)
table_rem <- table_remaining(exp_directory)
html_output <- knitr::opts_knit$get("rmarkdown.pandoc.to") %in% c("slidy", 'html')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("./../")
source('functions/params.R')
source('functions/import_results.R')
source('diagrams/cases.R')
source("diagrams/architecture.R")
source("diagrams/functionalities.R")
source('functions/exampleDT.R')
source('functions/gantt_tasks.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
exp_directory2 = PATHS[['experiments']] %>% paste0('201802061201/')
gantt <- print_solution(exp_directory, max_resources = 10, width="100%", height="500px")
gantt_tasks <- print_tasks(exp_directory2, width="100%", height="200px", max_tasks = 5)
graphs_rem <- graph_remaining(exp_directory)
table_rem <- table_remaining(exp_directory)
html_output <- knitr::opts_knit$get("rmarkdown.pandoc.to") %in% c("slidy", 'html')
```
